Trajectories

### 2021-09-24 Rmd/report.Rmd
Add methods section and rename manuscript files

```{r participants_time, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>% 
  group_by(time_stamp, lp, dominant_language) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  group_by(lp, dominant_language) %>% 
  mutate(n = cumsum(n)) %>% 
  ggplot(aes(time_stamp, n, colour = interaction(lp, dominant_language, sep = " - "), fill = interaction(lp, dominant_language, sep = " - "))) +
  geom_line(size = 1) +
  labs(x = "Date", y = "Number of responses", colour = "LP - Dominant language") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
  )

@@

We initially fitted a null model (`fit_0`) than only included the predictors `age` and `frequency` as nuisance parameters, along with random intercepts by `id` and `item`, and random slopes of `frequency` by `id`, and `age` by `item`, and their correlation parameter. We then extended this model (`fit_1`) to include the main effect of `doe`, and the `doe` by `item` random slope. Finally, we added the main effect `cognate` (`fit_2`), its interaction with `doe` (`doe:cognate`), and  random slopes for `cognate` by `id`. The models were implemented in `brms` as:

@@

# emmeans
nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 50),
  lp = c("Monolingual", "Bilingual"),
  cognate = unique(items$cognate),
  frequency_center = c(-1, 0, 1)
)

m <- add_fitted_draws(nd, fits_comp_prior$fit_2, n = 20, re_formula = NA) %>% 
  mutate(frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")))

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_grid(lp~frequency_center) +
  geom_line(aes(group = interaction(.draw,  frequency_center, cognate)), alpha = 0.5) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.05) +
  # stat_summary(fun.data = "mean_se", geom = "pointrange") +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

# emmeans
nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 50),
  lp = c("Monolingual", "Bilingual"),
  cognate = unique(items$cognate),
  frequency_center = c(-1, 0, 1)
)

m <- add_fitted_draws(nd, fits_prod$fit_2, n = 20, re_formula = NA) %>% 
  mutate(frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")))

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_grid(lp~frequency_center) +
  geom_line(aes(group = interaction(.draw,  frequency_center, cognate)), alpha = 0.5) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.05) +
  # stat_summary(fun.data = "mean_se", geom = "pointrange") +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Production)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

```{r fixed_effects_table, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(fits_comp$fit_2)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercept", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="Intercept")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("age", "frequency", "doe", "cognate1", "doe:cognate1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  ) %>% 
  as_raw_html()

@@

```{r fix_effets_comp_plot, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Points and error bars in indicate the posterior means, and 50% and 95% CrI. The intercept has been transformed using the inverse logit to get the average probability of correct response. The resto of the coefficients has been transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable."}

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_lp1", "b_cognate1", "b_cognate2", "b_lp1:cognate1", "b_lp1:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "Lang. Profile (Bil. - Mon.)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "Lang. Profile \u00d7 Cognateness 1", "Lang. Profile \u00d7 Cognateness 2")
post <- gather_draws(fits_comp$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Comprehension posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```

@@

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_lp1", "b_cognate1", "b_cognate2", "b_lp1:cognate1", "b_lp1:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "Lang. Profile (Bil. - Mon.)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "Lang. Profile \u00d7 Cognateness 1", "Lang. Profile \u00d7 Cognateness 2")
post <- gather_draws(fits_prod$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Production posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```

@@

re_id <- ranef(fits_comp$fit_2)$id[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_comp$fit_2)[1])) %>% 
  left_join(distinct(fits_comp$fit_2$data, id, lp))

ggplot(re_id, aes(Estimate, reorder(id, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, colour = "white", height = 0) +
  geom_point(size = 0.5, colour = "white") +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Participant average probability of comprehension",
       y = "Participant") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )
```

@@

re_te <- ranef(fits_comp$fit_2)$te[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("te") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_comp$fit_2)[1])) %>% 
  mutate(te = as.numeric(te)) %>% 
  left_join(distinct(fits_comp$fit_2$data, te, lp))

ggplot(re_te, aes(Estimate, reorder(te, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, colour = "white", heigth = 0) +
  geom_point(size = 0.5, colour = "white") +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Item average probability of comprehension",
       y = "Item") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )
```

@@

re_id <- ranef(fits_prod$fit_2)$id[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_prod$fit_2)[1])) %>% 
  left_join(distinct(fits_prod$fit_2$data, id, lp))

ggplot(re_id, aes(Estimate, reorder(id, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, colour = "white", heigth = 0) +
  geom_point(size = 0.5, colour = "white") +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Item average probability of production",
       y = "Item") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )

@@

re_te <- ranef(fits_prod$fit_2)$te[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("te") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_prod$fit_2)[1])) %>% 
  mutate(te = as.numeric(te)) %>% 
  left_join(distinct(fits_prod$fit_2$data, te, lp))

ggplot(re_te, aes(Estimate, reorder(te, Estimate))) +
  geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, colour = "white", heigth = 0) +
  geom_point(size = 0.5, colour = "white") +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Item average probability of production",
       y = "Item") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(limits = c(0, 1)) +
  theme_github() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )
```

@@

nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 50),
  lp = c("Monolingual", "Bilingual"),
  cognate = unique(items$cognate),
  frequency_center = c(-1,  0, 1)
)

m <- add_fitted_draws(nd, fits_comp$fit_2, re_formula = NA, n = 25) %>% 
  mutate(frequency_center = as.factor(paste0(frequency_center, " SD")))

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_wrap(lp~frequency_center) +
  geom_line(aes(group = interaction(.draw, frequency_center, cognate)), alpha = 0.5) +

  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 50),
  lp = c("Monolingual", "Bilingual"),
  cognate = unique(items$cognate),
  frequency_center = c(-1,  0, 1)
)

m <- add_fitted_draws(nd, fits_prod$fit_2, re_formula = NA, n = 25) %>% 
  mutate(frequency_center = as.factor(paste0(frequency_center, " SD")))

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_wrap(lp~frequency_center) +
  geom_line(aes(group = interaction(.draw, frequency_center, cognate)), alpha = 0.5) +

  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

>>>>

```{r participants_time, message=FALSE, warning=FALSE, paged.print=FALSE}
participants %>% 
  group_by(time_stamp, dominant_language) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  group_by(dominant_language) %>% 
  mutate(n = cumsum(n)) %>% 
  ggplot(aes(time_stamp, n, colour = dominant_language, fill = dominant_language)) +
  geom_line(size = 1) +
  labs(x = "Date", y = "Number of responses", colour = "Dominant language") +
  scale_y_continuous(breaks = seq(0, 250, 50)) +
  guides(colour = guide_legend(ncol = 2)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
  )

@@

We initially fitted a null model (`fit_0`) than only included the predictors `age` and `frequency` as nuisance parameters, along with random intercepts by `id` and `item`, and random slopes of `frequency` by `id`, and `age` by `item`, and their correlation parameter. We then expanded this model (`fit_1`) to include the main effect of `doe`, and the `doe` by `item` random slope. Finally, we added the main effect `cognate` (`fit_2`), its interaction with `doe` (`doe:cognate`), and  random slopes for `cognate` by `id`. The models were implemented in `brms` as:

@@

# emmeans
nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 30),
  doe_center = range(responses$doe_center),
  cognate = unique(items$cognate),
  frequency_center = 0
)

m <- add_fitted_draws(nd, fits_comp_prior$fit_2, n = 20, re_formula = NA) %>% 
  mutate(
    frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")),
    doe_center = factor(doe_center, levels = unique(nd$doe_center), labels = c("DoE: 0%", "DoE: 100%"))
  )

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_grid(~doe_center) +
  geom_line(aes(group = interaction(.draw,  frequency_center, cognate)), alpha = 0.5) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.05) +
  # stat_summary(fun.data = "mean_se", geom = "pointrange") +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Comprehension)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 30),
  doe_center = range(responses$doe_center),
  cognate = unique(items$cognate),
  frequency_center = 0
)

m <- add_fitted_draws(nd, fits_prod_prior$fit_2, n = 20, re_formula = NA) %>% 
  mutate(
    frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")),
    doe_center = factor(doe_center, levels = unique(nd$doe_center), labels = c("DoE: 0%", "DoE: 100%"))
  )

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_grid(~doe_center) +
  geom_line(aes(group = interaction(.draw,  frequency_center, cognate)), alpha = 0.5) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.05) +
  # stat_summary(fun.data = "mean_se", geom = "pointrange") +
  # stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "P(Production)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

```{r fixed_effects_table, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(fits_comp$fit_2)$fixed %>% 
  as.data.frame() %>%
  rownames_to_column("term") %>% 
  mutate(
    Estimate = ifelse(term=="Intercept", inv_logit_scaled(Estimate), Estimate/4),
    `l-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`l-95% CI`), `l-95% CI`/4),
    `u-95% CI` = ifelse(term=="Intercept", inv_logit_scaled(`u-95% CI`), `u-95% CI`/4),
    Est.Error = ifelse(term=="Intercept", inv_logit_scaled(Est.Error), Est.Error/4)
  ) %>% 
  gt() %>% 
  fmt_percent(2:5) %>% 
  fmt_number(6:6, decimals = 2) %>% 
  fmt_number(7:8, decimals = 0) %>% 
  cols_merge(vars("l-95% CI", "u-95% CI"), pattern = "[{1}, {2}]") %>% 
  cols_label(
    term = md("**Predictor**"),
    Estimate = md("**Mean**"),
    Est.Error = md("**SEM**"),
    "l-95% CI" = md("**95\\% CrI**"),
    Rhat = md("**Rhat**"),
    Bulk_ESS = md("**Bulk ESS**"),
    Tail_ESS = md("**Tail ESS**")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the inverse logit to get the average probability of correct response",
    locations = cells_body(columns = "term", rows = term=="Intercept")
  ) %>% 
  tab_footnote(
    footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
    locations = cells_body(columns = "term", rows = term %in% c("age", "frequency", "doe_center", "cognate1", "doe_center:cognate1"))
  ) %>% 
  tab_footnote(
    footnote = "ESS: Effective sample size",
    locations = cells_column_labels(columns = c("Bulk_ESS", "Tail_ESS"))
  ) %>% 
  cols_align(
    align = c("center"),
    columns = 2:4
  ) %>% 
  as_raw_html()

@@

```{r fix_effets_comp_plot, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Points and error bars in indicate the posterior means, and 50% and 95% CrI. The intercept has been transformed using the inverse logit to get the average probability of correct response. The rest of the coefficients has been transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable."}

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_doe_center", "b_cognate1", "b_cognate2", "b_doe_center:cognate1", "b_doe_center:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "DoE (0% vs. 100%)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "DoE \u00d7 Cognateness 1", "DoE \u00d7 Cognateness 2")
post <- gather_draws(fits_comp$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Comprehension posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent, breaks = seq(-0.15, 2, 0.05), limits = c(-0.15, 0.2)) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```

@@

var_levels <- c("b_Intercept", "b_age", "b_frequency_center", "b_doe_center", "b_cognate1", "b_cognate2", "b_doe_center:cognate1", "b_doe_center:cognate2")
var_labels <- c("Intercept", "Age (+1 month)", "Frequency (+1 SD)", "DoE (0% vs. 100%)", "Cognateness 1 (IDC+NIC - NC)", "Cognateness 2 (IDC -NIC)", "DoE \u00d7 Cognateness 1", "DoE \u00d7 Cognateness 2")
post <- gather_draws(fits_prod$fit_2, `b_.*`, regex = TRUE) %>% 
  mutate(
    .value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4),
    .variable = factor(.variable, levels = var_levels, labels = var_labels, ordered = TRUE)
  )

ggplot(post, aes(.value, fct_rev(.variable))) +
  geom_vline(xintercept = 0, size = 0.75, colour = "grey") +
  stat_pointinterval(colour = "white") +
  labs(x = "Comprehension posterior probability", y = "Variable", fill = "Variable") +
  scale_x_continuous(labels = percent, breaks = seq(-0.15, 2, 0.05), limits = c(-0.15, 0.2)) +
  theme_github() +
  theme(
    legend.position = "none",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0),
    axis.title.y = element_blank(),
    # axis.text = element_text(size = 7),
    panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.y = element_blank()
  )
```

@@

re_id <- ranef(fits_comp$fit_2)$id[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_comp$fit_2)[1])) %>% 
  left_join(distinct(fits_comp$fit_2$data, id, doe_center)) %>% 
  clean_names()

ggplot(re_id, aes(estimate, reorder(id, estimate), xmin = q2_5, xmax = q97_5)) +
  geom_ribbon(alpha = 0.5, colour = NA, fill = "white") +
  geom_line(aes(group = 1), size = 1, colour = "white") +
  # geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, height = 0) +
  # geom_point(size = 0.5) +
  geom_vline(group = 1, xintercept = 0.5, colour = "white") +
  labs(x = "Participant posterior probability of comprehension",
       y = "Participant", colour = "Lang. Prof.") +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )
```

@@

re_te <- ranef(fits_comp$fit_2)$te[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("te") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_comp$fit_2)[1])) %>% 
  mutate(te = as.numeric(te)) %>% 
  left_join(distinct(fits_comp$fit_2$data, te, cognate)) %>% 
  clean_names()

ggplot(re_te, aes(estimate, reorder(te, estimate), xmin = q2_5, xmax = q97_5, 
                  colour = cognate, fill = cognate)) +
  facet_wrap(~cognate, scales = "free_y", ncol = 2) +
  geom_ribbon(aes(group = cognate), alpha = 0.5, colour = NA) +
  geom_line(aes(group = cognate), size = 1) +
  # geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, height = 0) +
  # geom_point(size = 0.5) +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Item posterior probability of comprehension",
       y = "Item", colour = "Cognate") +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )

@@

re_id <- ranef(fits_prod$fit_2)$id[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("id") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_prod$fit_2)[1])) %>% 
  left_join(distinct(fits_prod$fit_2$data, id)) %>% 
  clean_names()

ggplot(re_id, aes(estimate, reorder(id, estimate), xmin = q2_5, xmax = q97_5)) +
  geom_ribbon(aes(group = 1), alpha = 0.5, colour = NA, fill = "white") +
  geom_line(aes(group = 1), size = 1, colour = "white") +
  # geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, height = 0) +
  # geom_point(size = 0.5) +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Participant posterior probability of production",
       y = "Participant", colour = "Lang. Prof.") +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )
```

@@

re_te <- ranef(fits_prod$fit_2)$te[,,1] %>% 
  as.data.frame() %>% 
  rownames_to_column("te") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, function(x) inv_logit_scaled(x + fixef(fits_prod$fit_2)[1])) %>% 
  mutate(te = as.numeric(te)) %>% 
  left_join(distinct(fits_prod$fit_2$data, te, cognate)) %>% 
  clean_names()

ggplot(re_te, aes(estimate, reorder(te, estimate), xmin = q2_5, xmax = q97_5, 
                  colour = cognate, fill = cognate)) +
  facet_wrap(~cognate, scales = "free_y", ncol = 2) +
  geom_ribbon(aes(group = cognate), alpha = 0.5, colour = NA) +
  geom_line(aes(group = cognate), size = 1) +
  # geom_errorbarh(aes(xmin = Q2.5, xmax = Q97.5), size = 0.25, height = 0) +
  # geom_point(size = 0.5) +
  geom_vline(xintercept = 0.5, colour = "white") +
  labs(x = "Item posterior probability of production",
       y = "Item", colour = "Cognate") +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme_github() +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_line(colour = "white", linetype = "dotted"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(colour = "white")
  )

@@

nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 30),
  doe_center = range(responses$doe_center),
  cognate = unique(items$cognate),
  frequency_center = 0
)

m <- add_fitted_draws(nd, fits_comp$fit_2, n = 20, re_formula = NA) %>% 
  mutate(
    frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")),
    doe_center = factor(doe_center, levels = unique(nd$doe_center), labels = c("DoE: 0%", "DoE: 100%"))
  )

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_wrap(~doe_center) +
  geom_line(aes(group = interaction(.draw, cognate), colour = cognate), alpha = 0.25) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  stat_summary(fun = "mean", geom = "line", size = 1) +  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "Posterior probability of comprehension\n(Linear prediction)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

@@

nd <- expand.grid(
  age = seq(min(responses$age), max(responses$age), length.out = 30),
  doe_center = range(responses$doe_center),
  cognate = unique(items$cognate),
  frequency_center = 0
)

m <- add_fitted_draws(nd, fits_prod$fit_2, n = 20, re_formula = NA) %>% 
  mutate(
    frequency_center = as.factor(paste0("Frequency = ", frequency_center, " SD")),
    doe_center = factor(doe_center, levels = unique(nd$doe_center), labels = c("DoE: 0%", "DoE: 100%"))
    )

ggplot(m, aes(age, .value, colour = cognate, fill = cognate)) +
  facet_wrap(~doe_center) +
  geom_line(aes(group = interaction(.draw, cognate), colour = cognate), alpha = 0.1, size = 1) +
  # stat_lineribbon(size = 0, alpha = 0.5, .width = 0.95) +
  stat_summary(fun = "mean", geom = "line", size = 1) +
  geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
  labs(x = "Age (months)", y = "Posterior probability of production\n(Linear prediction)", colour = "Cognateness", fill = "Cognateness") +
  scale_y_continuous(labels = scales::percent) +
  theme_github() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )
